\textbf{Varying coefficients correlated velocity models in complex landscapes with application to narwhal behavioral response to ship exposure and airgun exposure}

### 2024-05-28 Latex/main.tex
update Latex

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Coefficient   & Estimate  & $95\%$ CI \\
		\hline
		$\log(\tau_0)$   & 0     & 0.03 \\
		$\log(\nu_0)$  & 1.39  & -0.02 \\
		$\omega_0$     & 0     & -0.02 \\
		$\sigma_{\tau,pre}$   & 0.1   & 0.01  \\
		$\sigma_{\nu,pre}$    & 0.1   & 0.03  \\
		\hline
	\end{tabular}
	\caption{Intercepts baseline estimations}
	\label{table: baseline estilations}
\end{table}

>>>>

The persistence is estimated to $\hat{\tau}_{0}=1.3 $ h.
In comparison, harbour seal in Alaska were proved to exhibit slightly more persistent motion $\hat{\tau}=1.51$ h with $95\%$ CI ; $1.30 -1.75$  \cite{johnson_continuoustime_2008} while bowhead whales in Greenland showed much less persistence $\hat{\tau}=0.17$ h with $95\%$ CI ; $0.14 -0.20$  \cite{gurarie_correlated_2017}.
The intercept value for $\nu$ is estimated to be $\hat{\nu}_{0}=4.19$ km/h with $95\%$ CI $3.79-4.63$.
\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Coefficient   & Estimate  & $95\%$ CI \\
		\hline
		$\log(\tau_0)$   & 0.3    &  \\
		$\log(\nu_0)$  & 1.48  &  \\
		$\omega_0$     & -0.13     &  \\
		$\sigma_{\tau,pre}$   & 0.1   &   \\
		$\sigma_{\nu,pre}$    & 0.1   &  \\
		\hline
	\end{tabular}
	\caption{Intercepts baseline estimations}
	\label{table: baseline estilations}
\end{table}

Figure \ref{fig:febaseline3omegaanglenormalq0} shows the estimated smooth $\omega$ as a function of $\Theta$ for different values of the distance to shore. As distance increases, the magnitude of the angular velocity decreases. 
% PUT ON THE SAME PLOT WITH DIFFERENT COLOR FOR EACH CURVE
\begin{figure}[H]
	\begin{subfigure}{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\linewidth]{"images/application/baseline/fe_baseline3_omega_AngleNormal_q0.95_ExpShore .png"}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\linewidth]{"images/application/baseline/fe_baseline3_omega_AngleNormal_q0.75_ExpShore .png"}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\centering
		\includegraphics[width=0.95\linewidth]{"images/application/baseline/fe_baseline3_omega_AngleNormal_q0.25_ExpShore .png"}
	\end{subfigure}
	\caption{}

	\label{fig:febaseline3omegaanglenormalq0}
\end{figure}
